### 2019-04-11 paper/paper.tex
added table with things

To collect our data for package usage in public projects, 
we turned to the Google BigQuery \code{github\_repos} data 
set\footnote{https://bigquery.cloud.google.com/dataset/bigquery-public-dat:github\_repos}.
From this data, we skimmed all projects and pulled those 
written in JavaScript, resulting in an initial total of 9,017,221 
repositories. Simply being written in JavaScript is not enough to detect
\code{npm} usage, so to find repositories using \code{npm} packages
we looked for projects that contained a \code{package.json} 
file. After confirming that the formatting of the file matched the \code{npm}
standard, we are able to confidently say that any remaining packages are 
using \code{npm} packages. With this criteria, we then compiled a list 
of [100,000 for now] project 
repositories from GitHub, a volume that we felt is likely to be an 
appropriate representation of all such public projects.
Using the \code{GitHub} platform API and the list of valid repository names 
from before, we cloned the GitHub repository for each project. With
this, we were then able to determine the date and time of every 
commit of the project, as well as the list of included \code{npm} packages
at the time of commit, as listed in every commit version of 
\code{package.json}. The results showed that on average a repository 
had 37.9 commits as well as [STATS HERE]. Ultimately, of the 9,017,221 
public \code{GitHub} projects written in JavaScript and the [NUMBER] of repositories
using \code{npm} packages, we randomly selected [NUMBER] repositories as
a representative data set for the analysis.

@@

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figures/new_vs_updates_by_month.pdf}
  \caption{Packages updated and packages created per month. Multiple updates per month are
  only counted once.}
  \label{npmGrowth}
\end{figure}

Created in 2009, \code{npm} has grown
rapidly in popularity and scope over the last ten years, and 
as of the original paper showed no signs of slowing down \cite{Wittern:2016}.
We investigate the state of the \code{npm} ecosystem
since September 1\textsuperscript{st} 2015, and look for any signs of deterioration in 
the health of the ecosystem. Periods of stagnating growth would suggest
that developer interest is waning, while steady activity would 
indicate that the ecosystem as a whole is healthy and will continue to
evolve. To search for these potential indicators in the \code{npm} package environment,
we investigate the number of packages created and updated over time, as well
as system-wide trends of dependencies within packages. In Figure \ref{npmGrowth},
we can observe that while \code{npm} is still growing, the speed at which new packages
are created has slowed from an exponential to a linear rate. Some other things of note 
include an observable spike in package creation and updates around March 2016, the month 
when developer Azer Koçulu removed his 273 packages (including the popular package 
\code{left-pad}) from \code{npm} and in doing so affected some packages such as 
\code{babel} and \code{atom}, and therefore a significant fraction of \emph{all} 
\code{Node.js} projects\footnote{https://blog.npmjs.org/post/141577284765/kik-left-pad-and-npm}
There is also a significant spike in package updates observed in the month of January 2019, caused 
by some source currently unknown to the authors [TRY TO FIGURE THIS ONE OUT].
[ADD CONCAVITY DATA]. Figure 2 [CURRENTLY MISSING][MORE DATA COMMENTARY].

@@

@@

\subsection{Relationships between Measures}
[NEEDS MORE DATA]

\subsection{Distinct Package Types}
[NEEDS MORE DATA]

\subsection{Popularity Over Time}
[NEEDS MORE DATA]

\subsubsection{Identifying Top Packages}
[NEEDS MORE DATA]

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figures/geo_mean_highest_pagerank.pdf}
  \caption{\code{npm} rank (PageRank) of the five packages with the lowest overall geometric mean}
  \label{topFive}
\end{figure}

\subsubsection{Popular Package Dynamics}
[NEEDS MORE DATA]

@@

\subsubsection{Comparing Popularities}
[NEEDS MORE DATA]

@@

\section{Version Numbering and Package Adoption}
[NEEDS MORE DATA]

\subsection{Attribution of Version Numbers}
[NEEDS MORE DATA]

\subsection{Adoption by Version Number}
[NEEDS MORE DATA]

@@

\section{Conclusion}
[NEEDS MORE DATA]

>>>>

\textbf{@Greg I'm gonna need you to put something here}

@@

Created in 2009, \code{npm} has grown
rapidly in popularity and scope over the last ten years, and 
as of the original paper showed no signs of slowing down \cite{Wittern:2016}.
We investigate the state of the \code{npm} ecosystem
since September 1\textsuperscript{st} 2015, and look for any signs of deterioration in 
the health of the ecosystem. Periods of stagnating growth would suggest
that developer interest is waning, while steady activity would 
indicate that the ecosystem as a whole is healthy and will continue to
evolve. To search for these potential indicators in the \code{npm} package environment,
we investigate the number of packages created and updated over time, as well
as system-wide trends of dependencies within packages. In figure 1 
[INSERT DATA COMMENTARY HERE]. Figure 2 [MORE DATA COMMENTARY].

@@

% TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
\begin{tabular}{c|c|c|c}
  Year & Top 10 & Top 100 & Top 250 \\
  \hline
  2010 & 13 & 103 & 253\\
  2011 & 25 & 297 & 701\\
  2012 & 6 & 46 & 136\\
  2013 & 3 & 38 & 114\\
  2014 & 1 & 40 & 96\\
  2015 & 4 & 38 & 86\\
  2016 & 4 & 29 & 62\\
  2017 & 0 & 12 & 48\\
  2018 & 0 & 15 & 31\\
  2019 & 0 & 4 & 12\\
\end{tabular}

@@

\subsection{Relationships between Measures}

\subsection{Distinct Package Types}

\subsection{Popularity Over Time}

\subsubsection{Identifying Top Packages}

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figures/geo_mean_highest_pagerank.pdf}
  \caption{\code{npm} rank (PageRank) of the five packages with the lowest overall geometric mean}
  \label{geoMean}
\end{figure}

\subsubsection{Popular Package Dynamics}

@@

\subsubsection{Comparing Popularities}

@@

\section{Version Numbering and Package Adoption}

\subsection{Attribution of Version Numbers}

\subsection{Adoption by Version Number}

@@

\section{Conclusion}
